Maximum Entropy Spectral Analysis

### 2021-02-18 paper/mesa.tex
second chunk edited

without highlighting its connection with the time structure of the process itself, thus masking some important properties that will explore further in what follows. The latter definition in (\ref{eq:psd-f-definition}) gives, however, i) a straightforward interpretation of the PSD: it measures how much signal ``power" is located in each frequency; ii) an operative way of estimating for an unknown process.  

@@

An ubiquitous method for such computation is due to Welch \cite{Welch} and it based on the method of periodograms. Basically, the PSD is obtained by slicing the observed realisation $x(t_1),\ldots,x(t_n)$ of the process $x(t)$ into many windowed batches and averaging the squared moduli of their Fourier transforms. The standard approach of periodograms \cite{Lomb,Scargle} consists in taking the Fourier Transform of the sample autocorrelation, written as \begin{equation}

@@

\section{Theoretical foundations}
The Maximum Entropy principle (MAXENT) is among the most important results in Bayesian Statistics. It provides a way to uniquely assign probabilities to a phenomenon in a way that best represent our state of knowledge, while at the same time it is non committal with unavailable information. Its domain of application turned out to be wider than expected. In fact, thanks to Burg \cite{burg1975maximum}, this method has also been applied to perform high quality computation of power spectral densities of time series.

@@

\subsection{Maximum Entropy Principle} \label{sec:MAXENT}
\sschmidt{This section is yet to prune}
To introduce MAXENT as a variational problem, we will workout some simple examples to understand how information's entropy and `uncertainty' are related\footnote{
The word `information' will not be used to indicate our knowledge on the system under study: this is what we will call `evidence'. Information will be intended as in communication theory: it specifies the quantity of details needed to provide a full description of the system under study.
}.

If we consider a perfectly sinusoidal signal, knowledge of amplitude, frequency and phase are sufficient to fully reproduce it: it has a low information entropy content.
Even less information is required if we are studying a system whose outcome is certain (has probability $p = 1$).
If the amount of information $I$ can be considered to zero, a communication is not even needed.  
Shannon \cite{Shannon} proposed the quantity
\begin{equation}\label{eq:information}
    I = \log_2 \frac{1}{p(x)}
\end{equation}
to represent the quantity of information brought by an outcome $x$ with probability $p(x)$. It has the nice property of being an additive quantity and it is monotonically decreasing as a function of $p \in [0, 1]$. The more uncertain the outcome, the higher the information it brings.
\par
What happens if we consider a larger set of different events? What is  the `most uncertain' outcome?  Since we are intending probability as a representation of the state of knowledge, one of the first requirement for our assignment is the agreement with common sense.
Consider an experiment based on the occurrence of one of two different outcomes $E_1, E_2$ with given probabilities $P_1$ and $P_2$. What are the values that make our outcome the most uncertain?
If $P_1$ and $P_2$ are largely different, like $P_1 = 0.999$ and $P_2 = 0.001$, we have enough evidence to believe that event $E_1$ will occur almost certainly, considering $E_2$ to be a very implausible outcome.
The most unpredictable experiment is the one in which 
\begin{equation}\nonumber
    P_1 = P_2 = \frac{1}{2}:
\end{equation}
this describes a situation of `maximum ignorance'; we have no evidence at all and we have no instruments to predict what the outcome of such an experiment will be.  \\ 
This can be generalized in the case of $N$ events. Assigning same probability
\begin{equation*}
    P_1 = \dots = P_N = \frac{1}{N}
\end{equation*}
for each outcome, i.e. appealing to the indifference principle (IP), is equivalent to the requirement for our experiment to be the most unpredictable. 
All we know is that one over $N$ events is going to happen. With this evidence, we cannot expect one outcome to occur over the others. 
To report the results of such an experiment, we need to communicate every single outcome: it 'carries' high information. 
This description also makes clearer the role played by evidence: it has to be used in probability assignment in order to make the result 'more certain' or 'less informative'. It is clear from the point of view of communication theory: the higher the evidence on a system, the lower the information I need to send to describe it.
\par
It is now clear that any assignment different from the 'most uncertain' is violating the hypothesis for it to being non committal to non-available evidence. We can only assign a more certain probability, i.e. less informative, if we have evidence for it. If we have none, the result has to be the most unpredictable, i.e. the most informative. 
Assigning probabilities requires maximization of uncertainty using evidence as constraint. This looks like a variational problem, where a numerical measure of uncertainty $H\left[p_1, \dots, p_N\right]$ has to maximized. $H$ has to be a 'generalization' of information defined in equation (\ref{eq:information}) to be something like the 'expected information' brought by an experiment with $N$ possible outcomes each with its own probability $p_i$.

Some properties for $H$ can be worked out easily. 
From previous discussion, given a fixed number $N$ of possible outcomes, we want $H$ to be maximized by the choice $p_1 = \dots = p_N$.
Consider now the opposite situation, in which probability is assigned appealing to IP and we have a different number of possible outcomes.
Intuitively, the most unpredictable experiment is the one with larger number of outcomes: probability of "getting it wrong" increases as $\frac{N -1}{N}$. So when equal probabilities are assigned, we want
\begin{equation}
    \nonumber
    H\left[\frac{1}{N}, \dots, \frac{1}{N}\right]
\end{equation}
to increase monotonically with N.

We also want our function to be continuous in its parameters: any small change in probability has to slightly affect uncertainty. \\
Last is composition property. Consider three events with probability $p_1, p_2, p_3$ such that $p_2 + p_3 = 1 - p_1 = q$. We require 
\begin{equation}
    H\left(p_1, p_2, p_3\right) = H(p_1, q) + qH\left(\frac{p_2}{q}, \frac{p_3}{q}\right),
\end{equation}
so that uncertainty is additive.

Shannon \cite{Shannon} showed that the only functional form satisfying our assumptions is given by:
\begin{equation}\label{eq:entropy}
    H[p_1, \dots, p_N] = - \sum_{i = 1}^N p_i\log{p_i},
\end{equation}
or, in the continuous case:
\begin{equation}
    H[p(x)] = - \int p(x)\ln p(x) dx,
\end{equation}
and $H$ is what we will call entropy.

This interpretation is straigthforward: if we compare it with Eq.~(\ref{eq:information}), we see that the entropy is defined as the 'average information'. The probability assignments made maximizing it with respect to $p$, is somehow requiring  the 'expected value' of uncertainty to be a maximum. Such an assignment is in agreement with our hypothesis of being `non committal' with unavailable evidence, since \ref{eq:entropy} is all we need to assign probabilities uniquely. Evidence can be added in form of constraints in the maximization.

%It is easy to verify that this expression for entropy verifies the aforementioned properties. 
%Assigning the same value for each probability $p_i$, it is straightforward to verify $H$ increases with N: 
%\begin{equation}
%    -\sum_{i = 1}^N \frac{1}{N}\log{\frac{1}{N}} = - \log\frac{1}{N} = \log N.
%\end{equation}

To show how the maximization of entropy, supplemented with additional evidence, can provide a unique probability assignment, we will work out three examples.
In each of them, we will add more evindence (i.e. constraints on the optimization problem) and we will obtain different results.

First of all, we want to show that, in case in which our only constraint is exhaustiveness
$\sum_{i = 1}^{N}p_i = 1 $,
MAXENT reduces to indifference principle as it should be. The variational problem is defined as
\begin{equation}\label{eq:entropyNormConst}
    \delta\left[H - \lambda\sum_{i = 1}^N (p_i - 1)\right] = 0 
\end{equation}
with
\begin{equation}
    \delta H\left[p_1, \dots, p_N\right] = \sum_{i = 1}^N\frac{\partial H}{\partial p_i}\delta p_i = - \sum_{i = 1}^N\left(\log p_i + 1\right),
\end{equation}
so that equation \ref{eq:entropyNormConst} reduce to
\begin{equation}\nonumber 
    \sum_{i = 1}^N\left[\log p_i + \lambda + 1 \right]\delta p_i = 0\,.
\end{equation}
The solution of the previous equation is easily worked out requiring every term to be zero: 
\begin{equation}\nonumber 
    p_i = e^{-\lambda - 1}.
\end{equation}
Applying the normalization condition, it is immediate to show that
\begin{equation}
    p_i = \frac{1}{N}.
\end{equation}
MAXENT reduces to the IP when only the normalization constraint is used.

In the second example, we will add the constraint that the distribution has a known mean value: $\int \d{x} x p(x) = \bar{x}$. For simplicity we will work in the continuous case.
The variational problem can be rewritten as: 
\begin{equation}
    \int \left[\log p(x) + 1 + \lambda + \mu x \right]\delta p(x) = 0
\end{equation}
with constraints: 
\begin{equation*}
    \int \d{x} \; p(x)  = 1 \text{  and  }
    \int \d{x} \; x p(x) = \bar x.
\end{equation*}
For simplicity, we consider $x$ to be a variable ranging in the interval $(-\infty,+\infty)$, but this can be easily computed for every other interval.

The general solution for $p(x)$ is:
\begin{equation}
    p(x) = e^{-1 - \lambda - \mu x} 
\end{equation}
where $\lambda$ and $\mu$ are two Lagrange multipliers
The normalization conditions implies 
\begin{equation}\nonumber 
   1 =  \int \d{x} \; p(x) = e^{-1-\lambda}\int e^{-\mu x} dx, 
\end{equation}
so that: 
\begin{equation}\nonumber 
    e^{-1 -\lambda} = \mu.
\end{equation}
The fixed average condition provides a value for $\mu$ in terms of $\bar{x}$:
\begin{equation}
	\mu = \frac{1}{\bar{x}}
\end{equation}
The solution is then an exponential distribution:
\begin{equation}
    p(x) = \frac{1}{\bar{x}} \exp\left(-\frac{x}{\bar{x}}\right). \nonumber 
\end{equation}

Lastly, and more interestingly, we also consider a constraint on the variance. For this reason, we set:
\begin{align*}
    \int \d{x} \; p(x)  = 1 \text{  and  }
	\int \d{x} \; x p(x) = \bar{x} \\
	\text{  and  }
	\int \d{x} \; (x-\bar{x})^2 p(x)  = \sigma^2
\end{align*}
Performing the same computation as above, we obtain a well known result:
\begin{equation}
	p(x) = \frac{1}{\sigma\sqrt{2\pi}} e^{-\frac{1}{2}\left(\frac{x-\bar{x}}{\sigma}\right)^2}
\end{equation}

%Take a vector  $\vec x(t)$ with components in $\mathbb{R}^N$
%\begin{equation*}
%    \vec x(t) = \left(x_1, \dots, x_N \right), \quad \text{ with } x_i = x(t_i),
%\end{equation*}
%We assume $\vec x$ to be time dependent and real valued because we will work with time dependent single channel signals. If we put constraints in both mean $\vec \mu(t)$ and covariance matrix $C_(t_i, t_j)$, MAXENT allow us to assign for $\vec x(t)$ a multivariate normal distribution \cite{gregory_2005}: 
%\begin{align}
%    p&\left(\vec x(t)\vert I\right) = \nonumber \\
%    &\frac{1}{\left(2 \pi \det C\right)^{k / 2}}\exp\left(-\frac{1}{2}\sum_{i,j}(x_i-\mu_i) (x_j-\mu_j)C^{-1}_{ij} \right). 
%\end{align}
Thus MAXENT provide a deeper insight into the Gaussian distribution.
It is not only the limit distribution provided by the central limit theorem for finite variance processes but it is also the distribution that maximizes the entropy. For this reason, appealing to MAXENT principle, it is the correct assignment if mean and covariance are the only quantities that fully define our process. In some sense, we can interpret the central limit theorem as the natural `statistical' evolution toward a configuration that maximizes entropy.

\subsection{Maximum Entropy Spectral Analysis} \label{sec:MESA}
The computation of the power spectral density is an important component in stationary time series analysis and characterization.
In principle, if the autocorrelation was known exactly (i.e. at every time $\tau$), the computation of the PSD would be just a single Fourier transform.
However, in every realistic setting, we are dealing with a finite number of samples $N$ and it is not possible such precise computation.
Moreover, the error $\sigma_k$ in the estimate of the autocorrelation after $k$ steps increases with $k$ as $\sigma \sim \frac{1}{\sqrt{N - k}}$, so that only a few values for the autocorrelation function can actually be computed reliably.
This bring us the core of our problem: how to give an estimate from partial (and noisy) knowledge of the autocorrelation function? The Maximum Entropy Principle can guide use in this task without any a priori assumptions on the unavailable data\footnote{Indeed this is the largest difference with the most common Welch method. The latter assumes that the unknown values of the autocorrelation are $0$. Clearly, this assumption is unjustified and MAXENT is a good way to drop this assumption.}.
\par
As in the previous examples, we need to set up a variational problem where the entropy eq.~\ref{eq:entropy} is maximized with some problem-specific constraints. 
In our case, they are i) the PSD estimate has to be non-negative; ii) its Fourier transform has to match the sample autocorrelation (wherever an estimate of this is available).
\par
Before doing so, there is a technical problem to solve: our definition of entropy (eq.~\ref{eq:entropy}) depends on a probability distribution, not on the power spectrum. We then need to to formulate the variational problem in terms of the power spectral density $S(f)$ alone.
A way out of this is considering our signal as the result of filtering a white noise process with a filter whose power response is exactly $S(f)$ \cite{AblesMESA}. One can show that the 'entropy gain' obtained filtering white noise is: 
\begin{equation}\label{eq:EntropyGain}
    \Delta H = \int_{-\infty}^{\infty}\log S(f) df , 
\end{equation}
so that we can reformulate the variational problem requiring $S(f)$ to maximize the entropy gain \sschmidt{Non ho capito questa parte...:(}. In real examples we have no access to all frequencies but only on those between minus and plus the Nyquist frequency, defined from the sampling interval $\Delta t$ as 
\begin{equation}
    Ny = \frac{1}{2 \Delta t}.
\end{equation}
All our quantities are well defined in this range only, so that we are not going to maximize \ref{eq:EntropyGain}, but
\begin{equation}\label{eq:EntropyGain2}
    \Delta H = \int_{- Ny}^{Ny}\log S(f) df.
\end{equation}

@@

@@

\section{Example} 
=======
\subsection{Analysis of the optimizers}

\subsection{Comparison with Welch method}

\section{Examples}

	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% END & BIB
>>>>>>> dc2ea6b02d554f80ea49ef0c67cf14dcffc60bb8

>>>>

without highlighting its connection with the time structure of the process itself, thus masking some important properties that will explore further in what follows. The latter definition in (\ref{eq:psd-f-definition}) gives, however, i) a straightforward interpretation of the PSD: it measures how much signal ``power" is located in each frequency; ii) an operative way of estimating it for an unknown process.  

@@

A ubiquitous method for such computation is due to Welch \cite{Welch} and it based on the method of periodograms. Basically, the PSD is obtained by slicing the observed realisation $x(t_1),\ldots,x(t_n)$ of the process $x(t)$ into many windowed batches and averaging the squared moduli of their Fourier transforms. The standard approach of periodograms \cite{Lomb,Scargle} consists in taking the Fourier Transform of the sample autocorrelation, written as \begin{equation}

@@

\section{Theoretical foundations}
The Maximum Entropy principle (MAXENT) is among the most important results in Bayesian probability theory. It provides a way to uniquely assign probabilities to a phenomenon in a way that best represent our state of knowledge, while at the same time it is non committal with unavailable information. Its domain of application turned out to be wider than expected. In fact, thanks to Burg \cite{burg1975maximum}, this method has also been applied to perform high quality computation of power spectral densities of time series.

@@

\subsection{Maximum Entropy Principle} \label{sec:MAXENT}
\sschmidt{This section is yet to prune}
Before introducing MAXENT as a variational problem, we will workout some simple examples to contexualise how information's entropy
and `uncertainty' are related. First of all,  it is worth noting that the word `information' will not be used to indicate our knowledge on the system under study: this is what we will call `evidence'. Information will be intended as in communication theory: it specifies the length of the message necessary to provide
a full description of the system under study.

For instance, consider a perfectly sinusoidal signal: knowledge of amplitude, frequency and phase are sufficient to fully reproduce it: 
it has a low information entropy content. Even less information is required if we are studying a system whose outcome is 
certain (has probability $p = 1$). If the amount of information $I$ can be considered to zero, a communication is not even needed.  
    I = \log_2 \frac{1}{p(x)}
to represent the quantity of information brought by an outcome $x$ with probability $p(x)$. It is additive quantity as well as monotonically decreasing as a function of $p \in [0, 1]$. The more uncertain the outcome, the higher the information it brings.
What happens if we consider a larger set of different events? What is  the `most uncertain' outcome?  Since we are intending probability as a representation of the state of knowledge, one of the first requirement for our assignment is the agreement with common sense.
Consider an experiment based on the occurrence of one of two different outcomes $E_1, E_2$ with given probabilities $P_1$ and $P_2$. What are the values that make our outcome the most uncertain?
If $P_1$ and $P_2$ are largely different, like $P_1 = 0.999$ and $P_2 = 0.001$, we have enough evidence to believe that event $E_1$ will occur almost certainly, considering $E_2$ to be a very implausible outcome.
this describes a situation of `maximum ignorance'; we have no evidence at all and we have no way of predicting what the outcome of such an experiment will be.  The generalisation to $N$ possible outcomes is straightforward. \\ 
%This can be generalized in the case of $N$ events. Assigning same probability
%\begin{equation*}
%    P_1 = \dots = P_N = \frac{1}{N}
%\end{equation*}
%for each outcome, i.e. appealing to the indifference principle (IP), is equivalent to the requirement for our experiment to be the most unpredictable. 
%All we know is that one over $N$ events is going to happen. With this evidence, we cannot expect one outcome to occur over the others. 
%To report the results of such an experiment, we need to communicate every single outcome: it 'carries' high information. 
In this context, the role played by evidence should also be clear: it dictates the probability assignment in order to make the result 'more certain' or 'less informative'. Any assignment different from the 'most uncertain' is violating the principle of it to being non committal to non-available evidence. We can only assign a more certain probability, i.e. less informative, if we have evidence for it. If we have none, the result has to be the most unpredictable, i.e. the most informative. From the point of view of communication theory: the higher the evidence on a system, the lower the information I need to send to describe it.
MAXENT ratifies the aforementioned principle by stating that probabilities should be assigned by maximizing uncertainty using evidence as constraint. 
This defines a variational problem, where a numerical measure of uncertainty $H\left[p_1, \dots, p_N\right]$ has to maximized. $H$ has to be a 'generalization' of information defined in equation (\ref{eq:information}) to be something like the 'expected information' brought by an experiment with $N$ possible outcomes each with its own probability $p_i$.
%
%Some properties for $H$ can be worked out easily. 
%From previous discussion, given a fixed number $N$ of possible outcomes, we want $H$ to be maximized by the choice $p_1 = \dots = p_N$.
%Consider now the opposite situation, in which probability is assigned appealing to IP and we have a different number of possible outcomes.
%Intuitively, the most unpredictable experiment is the one with larger number of outcomes: probability of "getting it wrong" increases as $\frac{N -1}{N}$. So when equal probabilities are assigned, we want
%    \nonumber
%    H\left[\frac{1}{N}, \dots, \frac{1}{N}\right]
%to increase monotonically with N.
%
%We also want our function to be continuous in its parameters: any small change in probability has to slightly affect uncertainty. \\
%Last is composition property. Consider three events with probability $p_1, p_2, p_3$ such that $p_2 + p_3 = 1 - p_1 = q$. We require 
%    H\left(p_1, p_2, p_3\right) = H(p_1, q) + qH\left(\frac{p_2}{q}, \frac{p_3}{q}\right),
%so that uncertainty is additive.

Shannon \cite{Shannon} showed that the only functional form satisfying continuity with respect to its parameters and additivity is:
\begin{equation}\label{eq:entropy}
    H[p_1, \dots, p_N] = - \sum_{i = 1}^N p_i\log{p_i},
\end{equation}
or, in the continuous case:
\begin{equation}
    H[p(x)] = - \int p(x)\ln p(x) dx,
\end{equation}
and $H$ is what we will call (information) entropy.

%This interpretation is straightforward: if we compare it with Eq.~(\ref{eq:information}), we see that the entropy is defined as the 'average information'. The probability assignments made maximizing it with respect to $p$, is somehow requiring  the 'expected value' of uncertainty to be a maximum. Such an assignment is in agreement with our hypothesis of being `non committal' with unavailable evidence, since \ref{eq:entropy} is all we need to assign probabilities uniquely. Evidence can be added in form of constraints in the maximization.

%It is easy to verify that this expression for entropy verifies the aforementioned properties. 
%Assigning the same value for each probability $p_i$, it is straightforward to verify $H$ increases with N: 
%\begin{equation}
%    -\sum_{i = 1}^N \frac{1}{N}\log{\frac{1}{N}} = - \log\frac{1}{N} = \log N.
%\end{equation}
\wdp{I need to review and correct the following}
To show how the maximization of entropy, supplemented with additional evidence, can provide a unique probability assignment, 
we use a simple, pedagogical example. Consider the case in which we want assign a probability distribution $p(x)$ to a variable $x$ 
for which we know mean $\mu$ and covariance $\Sigma$. Our `evidence' is then coded as the following constraints:
\begin{align}
$\sum_{i = 1}^{N}p_i &= 1 $\\
$\sum_{i = 1}^{N}x_i p_i &= \mu $\\
$\sum_{i = 1}^{N}(x_i - \mu)(x_j - \mu) p_i &= \Sigma$\,
\end{align}
where the first row states the requirement of exhaustivity.
\wdp{i think we want the multivariate case since i) the gaussian case is also on wikipedia ii) we actually will need that  later on.}

%First of all, we want to show that, in case in which our only constraint is exhaustiveness
%$\sum_{i = 1}^{N}p_i = 1 $,
%MAXENT reduces to indifference principle as it should be. The variational problem is defined as
%\begin{equation}\label{eq:entropyNormConst}
%    \delta\left[H - \lambda\sum_{i = 1}^N (p_i - 1)\right] = 0 
%\end{equation}
%with
%\begin{equation}
%    \delta H\left[p_1, \dots, p_N\right] = \sum_{i = 1}^N\frac{\partial H}{\partial p_i}\delta p_i = - \sum_{i = 1}^N\left(\log p_i + 1\right),
%\end{equation}
%so that equation \ref{eq:entropyNormConst} reduce to
%\begin{equation}\nonumber 
%    \sum_{i = 1}^N\left[\log p_i + \lambda + 1 \right]\delta p_i = 0\,.
%\end{equation}
%The solution of the previous equation is easily worked out requiring every term to be zero: 
%\begin{equation}\nonumber 
%    p_i = e^{-\lambda - 1}.
%\end{equation}
%Applying the normalization condition, it is immediate to show that
%\begin{equation}
%    p_i = \frac{1}{N}.
%\end{equation}
%MAXENT reduces to the IP when only the normalization constraint is used.
%
%In the second example, we will add the constraint that the distribution has a known mean value: $\int \d{x} x p(x) = \bar{x}$. For simplicity we will work in the continuous case.
%The variational problem can be rewritten as: 
%\begin{equation}
%    \int \left[\log p(x) + 1 + \lambda + \mu x \right]\delta p(x) = 0
%\end{equation}
%with constraints: 
%\begin{equation*}
%    \int \d{x} \; p(x)  = 1 \text{  and  }
%    \int \d{x} \; x p(x) = \bar x.
%\end{equation*}
%For simplicity, we consider $x$ to be a variable ranging in the interval $(-\infty,+\infty)$, but this can be easily computed for every other interval.
%
%The general solution for $p(x)$ is:
%\begin{equation}
%    p(x) = e^{-1 - \lambda - \mu x} 
%\end{equation}
%where $\lambda$ and $\mu$ are two Lagrange multipliers
%The normalization conditions implies 
%\begin{equation}\nonumber 
%   1 =  \int \d{x} \; p(x) = e^{-1-\lambda}\int e^{-\mu x} dx, 
%\end{equation}
%so that: 
%\begin{equation}\nonumber 
%    e^{-1 -\lambda} = \mu.
%\end{equation}
%The fixed average condition provides a value for $\mu$ in terms of $\bar{x}$:
%\begin{equation}
%	\mu = \frac{1}{\bar{x}}
%\end{equation}
%The solution is then an exponential distribution:
%\begin{equation}
%    p(x) = \frac{1}{\bar{x}} \exp\left(-\frac{x}{\bar{x}}\right). \nonumber 
%\end{equation}

%Lastly, and more interestingly, we also consider a constraint on the variance. For this reason, we set:
%\begin{align*}
%    \int \d{x} \; p(x)  = 1 \text{  and  }
%	\int \d{x} \; x p(x) = \bar{x} \\
%	\text{  and  }
%	\int \d{x} \; (x-\bar{x})^2 p(x)  = \sigma^2
%\end{align*}
%Performing the same computation as above, we obtain a well known result:
%\begin{equation}
%	p(x) = \frac{1}{\sigma\sqrt{2\pi}} e^{-\frac{1}{2}\left(\frac{x-\bar{x}}{\sigma}\right)^2}
%\end{equation}

Take a vector  $\vec x(t)$ with components in $\mathbb{R}^N$
\begin{equation*}
    \vec x(t) = \left(x_1, \dots, x_N \right), \quad \text{ with } x_i = x(t_i),
\end{equation*}
We assume $\vec x$ to be time dependent and real valued because we will work with time dependent single channel signals. If we put constraints in both mean $\vec \mu(t)$ and covariance matrix $C_(t_i, t_j)$, MAXENT allow us to assign for $\vec x(t)$ a multivariate normal distribution \cite{gregory_2005}: 
\begin{align}
    p&\left(\vec x(t)\vert I\right) = \nonumber \\
    &\frac{1}{\left(2 \pi \det C\right)^{k / 2}}\exp\left(-\frac{1}{2}\sum_{i,j}(x_i-\mu_i) (x_j-\mu_j)C^{-1}_{ij} \right). 
\end{align}

Thus MAXENT provide a deeper insight into the Gaussian distribution.
It is not only the limit distribution provided by the central limit theorem for finite variance processes but it is also the distribution that maximizes the entropy. For this reason, appealing to MAXENT principle, it is the correct assignment if mean and covariance are the only quantities that fully define our process. In some sense, we can interpret the central limit theorem as the natural `statistical' evolution toward a configuration that maximizes entropy.

\subsection{Maximum Entropy Spectral Analysis} \label{sec:MESA}
The computation of the power spectral density is an important component in time series analysis and characterization.
In principle, if the autocorrelation was known exactly (i.e. at every time $\tau \in (-\infty,+\infty)$), the computation of the PSD 
would reduce to a single Fourier transform.
However, in any realistic setting, we are dealing with a finite number of samples $N$ from the process, hence such computation
is impossible.
Moreover, the error $\sigma_k$ in the estimate of the autocorrelation after $k$ steps increases with $k$ as $\sigma \sim \frac{1}{\sqrt{N - k}}$, so that only a few values for the autocorrelation function can actually be computed reliably.
This bring us the core of our problem: how to give an estimate from partial (and noisy) knowledge of the autocorrelation function? The Maximum Entropy Principle can guide use in this task without any a priori assumptions on the unavailable data\footnote{Indeed this is the largest difference with the most common Welch method. The latter assumes that the unknown values of the autocorrelation are $0$. Clearly, this assumption is unjustified and MAXENT is a good way to drop this assumption.}.
\par
As in the previous examples, we need to set up a variational problem where the entropy eq.~\ref{eq:entropy} is maximized with some problem-specific constraints. 
In our case, they are i) the PSD estimate has to be non-negative; ii) its Fourier transform has to match the sample autocorrelation (wherever an estimate of this is available).
\par
Before doing so, there is a technical problem to solve: our definition of entropy (eq.~\ref{eq:entropy}) depends on a probability distribution, not on the power spectrum. We then need to to formulate the variational problem in terms of the power spectral density $S(f)$ alone.
A way out of this is considering our signal as the result of filtering a white noise process with a filter whose power response is exactly $S(f)$ \cite{AblesMESA}. One can show that the 'entropy gain' obtained filtering white noise is: 
\begin{equation}\label{eq:EntropyGain}
    \Delta H = \int_{-\infty}^{\infty}\log S(f) df , 
\end{equation}
so that we can reformulate the variational problem requiring $S(f)$ to maximize the entropy gain \sschmidt{Non ho capito questa parte...:(}. In real examples we have no access to all frequencies but only on those between minus and plus the Nyquist frequency, defined from the sampling interval $\Delta t$ as 
\begin{equation}
    Ny = \frac{1}{2 \Delta t}.
\end{equation}
All our quantities are well defined in this range only, so that we are not going to maximize \ref{eq:EntropyGain}, but
\begin{equation}\label{eq:EntropyGain2}
    \Delta H = \int_{- Ny}^{Ny}\log S(f) df.
\end{equation}

@@

We will apply Burg method with each optimizer on a large amount of simulated dataset, obtaining a variety of estimate for PSD. We will study statistical properties for both single reproductions and ensemble average. In many cases, such as gravitational waves, one cannot observe multiple time series realizations for a fixed process, so that single reproduction studies are probably more useful. Still, study of ensemble average is important to highlight some interesting properties. In this way we can fully characterize the performance of each optimizer .

@@
